Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-29 docs/ms.tex
Update ms.tex

Weak gravitational lensing has become the most potential tool for constraining the cosmological parameters that describe the dark universe (Albrecht et al. 2006; Peacock & Schneider 2006). 
One application of Weak gravitational lensing is that it can be used to measure the mass profile of single galaxy,galaxy groups and clusters or large scales.
Cosmic shear is the mild distortion of distant galaxy images due to the bending of light by intervening matter.
Cosmic shear provides one of the most promising methods for constraining the nature of dark energy (Albrecht et al. 2006; Peacock&Schneider 2006). 
In galaxy--galaxy weaklensing  ,tangential shear distortions of background galaxies around foreground
galaxies, allows direct measurement of the galaxy–DM correlation

>>>>

Weak gravitational lensing has become the most potential tool to explore the dark universe. 
One application of Weak gravitational lensing is that it can be used to measure the mass profile of single galaxy,galaxy groups and clusters or large scales.
Cosmic shear is the mild distortion of distant galaxy images due to the bending of light by intervening matter.It provides one of the most promising methods for constraining the nature of dark energy (Albrecht et al. 2006; Peacock&Schneider 2006). 
While in galaxy--galaxy weaklensing ,tangential shear distortions of background galaxies around foreground galaxies, allows direct measurement of the galaxy–DM correlation
